### 2022-09-05 paper/ase22/tables/test-results-3-50-numbers.tex
final paper

\DefMacro{test-results-3-50-model0-lc7-num-seed-fail-avg}{24.0}
\DefMacro{test-results-3-50-model0-lc7-num-seed-fail-med}{24.0}
\DefMacro{test-results-3-50-model0-lc7-num-seed-fail-std}{5.0}
\DefMacro{test-results-3-50-model0-lc7-num-exp-fail-avg}{24.58}
\DefMacro{test-results-3-50-model0-lc7-num-exp-fail-med}{21.87}
\DefMacro{test-results-3-50-model0-lc7-num-exp-fail-std}{3.41}

@@

\DefMacro{test-results-3-50-model0-lc3-num-seed-fail-avg}{89.33}
\DefMacro{test-results-3-50-model0-lc3-num-seed-fail-med}{88.0}
\DefMacro{test-results-3-50-model0-lc3-num-seed-fail-std}{1.155}
\DefMacro{test-results-3-50-model0-lc3-num-exp-fail-avg}{90.63}
\DefMacro{test-results-3-50-model0-lc3-num-exp-fail-med}{89.87}
\DefMacro{test-results-3-50-model0-lc3-num-exp-fail-std}{0.705}

@@

\DefMacro{test-results-3-50-model0-lc4-num-seed-fail-avg}{92.31}
\DefMacro{test-results-3-50-model0-lc4-num-seed-fail-med}{92.31}
\DefMacro{test-results-3-50-model0-lc4-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model0-lc4-num-exp-fail-avg}{93.04}
\DefMacro{test-results-3-50-model0-lc4-num-exp-fail-med}{93.02}
\DefMacro{test-results-3-50-model0-lc4-num-exp-fail-std}{0.035}

@@

\DefMacro{test-results-3-50-model0-lc6-num-seed-fail-avg}{84.67}
\DefMacro{test-results-3-50-model0-lc6-num-seed-fail-med}{88.0}
\DefMacro{test-results-3-50-model0-lc6-num-seed-fail-std}{3.785}
\DefMacro{test-results-3-50-model0-lc6-num-exp-fail-avg}{88.51}
\DefMacro{test-results-3-50-model0-lc6-num-exp-fail-med}{89.86}
\DefMacro{test-results-3-50-model0-lc6-num-exp-fail-std}{4.55}

@@

\DefMacro{test-results-3-50-model0-lc5-num-seed-fail-avg}{99.33}
\DefMacro{test-results-3-50-model0-lc5-num-seed-fail-med}{100.0}
\DefMacro{test-results-3-50-model0-lc5-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model0-lc5-num-exp-fail-avg}{99.73}
\DefMacro{test-results-3-50-model0-lc5-num-exp-fail-med}{99.94}
\DefMacro{test-results-3-50-model0-lc5-num-exp-fail-std}{0.205}

@@

\DefMacro{test-results-3-50-model0-lc9-num-seed-fail-avg}{76.67}
\DefMacro{test-results-3-50-model0-lc9-num-seed-fail-med}{80.0}
\DefMacro{test-results-3-50-model0-lc9-num-seed-fail-std}{3.785}
\DefMacro{test-results-3-50-model0-lc9-num-exp-fail-avg}{75.51}
\DefMacro{test-results-3-50-model0-lc9-num-exp-fail-med}{79.39}
\DefMacro{test-results-3-50-model0-lc9-num-exp-fail-std}{3.86}

@@

\DefMacro{test-results-3-50-model0-lc2-num-seed-fail-avg}{14.0}
\DefMacro{test-results-3-50-model0-lc2-num-seed-fail-med}{12.0}
\DefMacro{test-results-3-50-model0-lc2-num-seed-fail-std}{3.605}
\DefMacro{test-results-3-50-model0-lc2-num-exp-fail-avg}{15.77}
\DefMacro{test-results-3-50-model0-lc2-num-exp-fail-med}{13.7}
\DefMacro{test-results-3-50-model0-lc2-num-exp-fail-std}{5.195}

@@

\DefMacro{test-results-3-50-model0-lc0-num-seed-fail-avg}{78.95}
\DefMacro{test-results-3-50-model0-lc0-num-seed-fail-med}{78.95}
\DefMacro{test-results-3-50-model0-lc0-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model0-lc0-num-exp-fail-avg}{87.8}
\DefMacro{test-results-3-50-model0-lc0-num-exp-fail-med}{88.0}
\DefMacro{test-results-3-50-model0-lc0-num-exp-fail-std}{0.36}

@@

\DefMacro{test-results-3-50-model0-lc1-num-seed-fail-avg}{0.0}
\DefMacro{test-results-3-50-model0-lc1-num-seed-fail-med}{0.0}
\DefMacro{test-results-3-50-model0-lc1-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model0-lc1-num-exp-fail-avg}{1.38}
\DefMacro{test-results-3-50-model0-lc1-num-exp-fail-med}{1.28}
\DefMacro{test-results-3-50-model0-lc1-num-exp-fail-std}{0.25}

@@

\DefMacro{test-results-3-50-model0-lc8-num-seed-fail-avg}{4.67}
\DefMacro{test-results-3-50-model0-lc8-num-seed-fail-med}{4.0}
\DefMacro{test-results-3-50-model0-lc8-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model0-lc8-num-exp-fail-avg}{5.87}
\DefMacro{test-results-3-50-model0-lc8-num-exp-fail-med}{6.67}
\DefMacro{test-results-3-50-model0-lc8-num-exp-fail-std}{1.25}

@@

\DefMacro{test-results-3-50-model1-lc7-num-seed-fail-avg}{12.67}
\DefMacro{test-results-3-50-model1-lc7-num-seed-fail-med}{14.0}
\DefMacro{test-results-3-50-model1-lc7-num-seed-fail-std}{2.08}
\DefMacro{test-results-3-50-model1-lc7-num-exp-fail-avg}{20.97}
\DefMacro{test-results-3-50-model1-lc7-num-exp-fail-med}{15.97}
\DefMacro{test-results-3-50-model1-lc7-num-exp-fail-std}{5.215}

@@

\DefMacro{test-results-3-50-model1-lc3-num-seed-fail-avg}{86.0}
\DefMacro{test-results-3-50-model1-lc3-num-seed-fail-med}{84.0}
\DefMacro{test-results-3-50-model1-lc3-num-seed-fail-std}{1.73}
\DefMacro{test-results-3-50-model1-lc3-num-exp-fail-avg}{88.14}
\DefMacro{test-results-3-50-model1-lc3-num-exp-fail-med}{87.15}
\DefMacro{test-results-3-50-model1-lc3-num-exp-fail-std}{1.31}

@@

\DefMacro{test-results-3-50-model1-lc4-num-seed-fail-avg}{92.31}
\DefMacro{test-results-3-50-model1-lc4-num-seed-fail-med}{92.31}
\DefMacro{test-results-3-50-model1-lc4-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model1-lc4-num-exp-fail-avg}{93.31}
\DefMacro{test-results-3-50-model1-lc4-num-exp-fail-med}{93.33}
\DefMacro{test-results-3-50-model1-lc4-num-exp-fail-std}{0.14}

@@

\DefMacro{test-results-3-50-model1-lc6-num-seed-fail-avg}{74.67}
\DefMacro{test-results-3-50-model1-lc6-num-seed-fail-med}{74.0}
\DefMacro{test-results-3-50-model1-lc6-num-seed-fail-std}{3.51}
\DefMacro{test-results-3-50-model1-lc6-num-exp-fail-avg}{73.04}
\DefMacro{test-results-3-50-model1-lc6-num-exp-fail-med}{70.1}
\DefMacro{test-results-3-50-model1-lc6-num-exp-fail-std}{5.935}

@@

\DefMacro{test-results-3-50-model1-lc5-num-seed-fail-avg}{99.33}
\DefMacro{test-results-3-50-model1-lc5-num-seed-fail-med}{100.0}
\DefMacro{test-results-3-50-model1-lc5-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model1-lc5-num-exp-fail-avg}{99.4}
\DefMacro{test-results-3-50-model1-lc5-num-exp-fail-med}{99.26}
\DefMacro{test-results-3-50-model1-lc5-num-exp-fail-std}{0.2}

@@

\DefMacro{test-results-3-50-model1-lc9-num-seed-fail-avg}{78.0}
\DefMacro{test-results-3-50-model1-lc9-num-seed-fail-med}{78.0}
\DefMacro{test-results-3-50-model1-lc9-num-seed-fail-std}{5.0}
\DefMacro{test-results-3-50-model1-lc9-num-exp-fail-avg}{78.77}
\DefMacro{test-results-3-50-model1-lc9-num-exp-fail-med}{82.92}
\DefMacro{test-results-3-50-model1-lc9-num-exp-fail-std}{5.985}

@@

\DefMacro{test-results-3-50-model1-lc2-num-seed-fail-avg}{52.0}
\DefMacro{test-results-3-50-model1-lc2-num-seed-fail-med}{50.0}
\DefMacro{test-results-3-50-model1-lc2-num-seed-fail-std}{1.73}
\DefMacro{test-results-3-50-model1-lc2-num-exp-fail-avg}{46.53}
\DefMacro{test-results-3-50-model1-lc2-num-exp-fail-med}{43.06}
\DefMacro{test-results-3-50-model1-lc2-num-exp-fail-std}{4.615}

@@

\DefMacro{test-results-3-50-model1-lc0-num-seed-fail-avg}{89.47}
\DefMacro{test-results-3-50-model1-lc0-num-seed-fail-med}{89.47}
\DefMacro{test-results-3-50-model1-lc0-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model1-lc0-num-exp-fail-avg}{78.7}
\DefMacro{test-results-3-50-model1-lc0-num-exp-fail-med}{78.12}
\DefMacro{test-results-3-50-model1-lc0-num-exp-fail-std}{0.75}

@@

\DefMacro{test-results-3-50-model1-lc1-num-seed-fail-avg}{2.67}
\DefMacro{test-results-3-50-model1-lc1-num-seed-fail-med}{2.0}
\DefMacro{test-results-3-50-model1-lc1-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model1-lc1-num-exp-fail-avg}{2.8}
\DefMacro{test-results-3-50-model1-lc1-num-exp-fail-med}{0.94}
\DefMacro{test-results-3-50-model1-lc1-num-exp-fail-std}{1.66}

@@

\DefMacro{test-results-3-50-model1-lc8-num-seed-fail-avg}{5.33}
\DefMacro{test-results-3-50-model1-lc8-num-seed-fail-med}{6.0}
\DefMacro{test-results-3-50-model1-lc8-num-seed-fail-std}{1.53}
\DefMacro{test-results-3-50-model1-lc8-num-exp-fail-avg}{5.85}
\DefMacro{test-results-3-50-model1-lc8-num-exp-fail-med}{6.14}
\DefMacro{test-results-3-50-model1-lc8-num-exp-fail-std}{0.93}

@@

\DefMacro{test-results-3-50-model2-lc7-num-seed-fail-avg}{32.0}
\DefMacro{test-results-3-50-model2-lc7-num-seed-fail-med}{24.0}
\DefMacro{test-results-3-50-model2-lc7-num-seed-fail-std}{10.585}
\DefMacro{test-results-3-50-model2-lc7-num-exp-fail-avg}{31.45}
\DefMacro{test-results-3-50-model2-lc7-num-exp-fail-med}{33.91}
\DefMacro{test-results-3-50-model2-lc7-num-exp-fail-std}{5.245}

@@

\DefMacro{test-results-3-50-model2-lc3-num-seed-fail-avg}{83.33}
\DefMacro{test-results-3-50-model2-lc3-num-seed-fail-med}{84.0}
\DefMacro{test-results-3-50-model2-lc3-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model2-lc3-num-exp-fail-avg}{85.71}
\DefMacro{test-results-3-50-model2-lc3-num-exp-fail-med}{86.11}
\DefMacro{test-results-3-50-model2-lc3-num-exp-fail-std}{0.64}

@@

\DefMacro{test-results-3-50-model2-lc4-num-seed-fail-avg}{92.31}
\DefMacro{test-results-3-50-model2-lc4-num-seed-fail-med}{92.31}
\DefMacro{test-results-3-50-model2-lc4-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model2-lc4-num-exp-fail-avg}{95.66}
\DefMacro{test-results-3-50-model2-lc4-num-exp-fail-med}{95.41}
\DefMacro{test-results-3-50-model2-lc4-num-exp-fail-std}{0.25}

@@

\DefMacro{test-results-3-50-model2-lc6-num-seed-fail-avg}{87.33}
\DefMacro{test-results-3-50-model2-lc6-num-seed-fail-med}{88.0}
\DefMacro{test-results-3-50-model2-lc6-num-seed-fail-std}{3.51}
\DefMacro{test-results-3-50-model2-lc6-num-exp-fail-avg}{91.1}
\DefMacro{test-results-3-50-model2-lc6-num-exp-fail-med}{92.9}
\DefMacro{test-results-3-50-model2-lc6-num-exp-fail-std}{4.19}

@@

\DefMacro{test-results-3-50-model2-lc5-num-seed-fail-avg}{98.67}
\DefMacro{test-results-3-50-model2-lc5-num-seed-fail-med}{98.0}
\DefMacro{test-results-3-50-model2-lc5-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model2-lc5-num-exp-fail-avg}{98.44}
\DefMacro{test-results-3-50-model2-lc5-num-exp-fail-med}{99.11}
\DefMacro{test-results-3-50-model2-lc5-num-exp-fail-std}{0.99}

@@

\DefMacro{test-results-3-50-model2-lc9-num-seed-fail-avg}{80.67}
\DefMacro{test-results-3-50-model2-lc9-num-seed-fail-med}{84.0}
\DefMacro{test-results-3-50-model2-lc9-num-seed-fail-std}{9.61}
\DefMacro{test-results-3-50-model2-lc9-num-exp-fail-avg}{78.54}
\DefMacro{test-results-3-50-model2-lc9-num-exp-fail-med}{82.31}
\DefMacro{test-results-3-50-model2-lc9-num-exp-fail-std}{11.03}

@@

\DefMacro{test-results-3-50-model2-lc2-num-seed-fail-avg}{54.67}
\DefMacro{test-results-3-50-model2-lc2-num-seed-fail-med}{58.0}
\DefMacro{test-results-3-50-model2-lc2-num-seed-fail-std}{2.885}
\DefMacro{test-results-3-50-model2-lc2-num-exp-fail-avg}{55.97}
\DefMacro{test-results-3-50-model2-lc2-num-exp-fail-med}{60.67}
\DefMacro{test-results-3-50-model2-lc2-num-exp-fail-std}{4.6}

@@

\DefMacro{test-results-3-50-model2-lc0-num-seed-fail-avg}{100.0}
\DefMacro{test-results-3-50-model2-lc0-num-seed-fail-med}{100.0}
\DefMacro{test-results-3-50-model2-lc0-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model2-lc0-num-exp-fail-avg}{95.8}
\DefMacro{test-results-3-50-model2-lc0-num-exp-fail-med}{95.96}
\DefMacro{test-results-3-50-model2-lc0-num-exp-fail-std}{0.545}

@@

\DefMacro{test-results-3-50-model2-lc1-num-seed-fail-avg}{0.0}
\DefMacro{test-results-3-50-model2-lc1-num-seed-fail-med}{0.0}
\DefMacro{test-results-3-50-model2-lc1-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model2-lc1-num-exp-fail-avg}{0.92}
\DefMacro{test-results-3-50-model2-lc1-num-exp-fail-med}{0.94}
\DefMacro{test-results-3-50-model2-lc1-num-exp-fail-std}{0.24}

@@

\DefMacro{test-results-3-50-model2-lc8-num-seed-fail-avg}{5.33}
\DefMacro{test-results-3-50-model2-lc8-num-seed-fail-med}{6.0}
\DefMacro{test-results-3-50-model2-lc8-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model2-lc8-num-exp-fail-avg}{6.76}
\DefMacro{test-results-3-50-model2-lc8-num-exp-fail-med}{6.07}
\DefMacro{test-results-3-50-model2-lc8-num-exp-fail-std}{1.515}

>>>>

\DefMacro{test-results-3-50-model0-lc7-num-all-fail-avg}{375.0}
\DefMacro{test-results-3-50-model0-lc7-num-all-fail-med}{331}
\DefMacro{test-results-3-50-model0-lc7-num-all-fail-std}{38.54}
\DefMacro{test-results-3-50-model0-lc7-num-all-failrate-avg}{24.57}
\DefMacro{test-results-3-50-model0-lc7-num-all-failrate-med}{21.92}
\DefMacro{test-results-3-50-model0-lc7-num-all-failrate-std}{3.46}

@@

\DefMacro{test-results-3-50-model0-lc3-num-all-fail-avg}{1969.67}
\DefMacro{test-results-3-50-model0-lc3-num-all-fail-med}{1907}
\DefMacro{test-results-3-50-model0-lc3-num-all-fail-std}{105.065}
\DefMacro{test-results-3-50-model0-lc3-num-all-failrate-avg}{90.6}
\DefMacro{test-results-3-50-model0-lc3-num-all-failrate-med}{89.83}
\DefMacro{test-results-3-50-model0-lc3-num-all-failrate-std}{0.715}

@@

\DefMacro{test-results-3-50-model0-lc4-num-all-fail-avg}{1039.67}
\DefMacro{test-results-3-50-model0-lc4-num-all-fail-med}{1039}
\DefMacro{test-results-3-50-model0-lc4-num-all-fail-std}{8.005}
\DefMacro{test-results-3-50-model0-lc4-num-all-failrate-avg}{93.02}
\DefMacro{test-results-3-50-model0-lc4-num-all-failrate-med}{93.01}
\DefMacro{test-results-3-50-model0-lc4-num-all-failrate-std}{0.035}

@@

\DefMacro{test-results-3-50-model0-lc6-num-all-fail-avg}{1026.33}
\DefMacro{test-results-3-50-model0-lc6-num-all-fail-med}{934}
\DefMacro{test-results-3-50-model0-lc6-num-all-fail-std}{81.265}
\DefMacro{test-results-3-50-model0-lc6-num-all-failrate-avg}{88.35}
\DefMacro{test-results-3-50-model0-lc6-num-all-failrate-med}{89.86}
\DefMacro{test-results-3-50-model0-lc6-num-all-failrate-std}{4.5}

@@

\DefMacro{test-results-3-50-model0-lc5-num-all-fail-avg}{1523.0}
\DefMacro{test-results-3-50-model0-lc5-num-all-fail-med}{1384}
\DefMacro{test-results-3-50-model0-lc5-num-all-fail-std}{129.575}
\DefMacro{test-results-3-50-model0-lc5-num-all-failrate-avg}{99.72}
\DefMacro{test-results-3-50-model0-lc5-num-all-failrate-med}{99.95}
\DefMacro{test-results-3-50-model0-lc5-num-all-failrate-std}{0.22}

@@

\DefMacro{test-results-3-50-model0-lc9-num-all-fail-avg}{1174.67}
\DefMacro{test-results-3-50-model0-lc9-num-all-fail-med}{1181}
\DefMacro{test-results-3-50-model0-lc9-num-all-fail-std}{135.78}
\DefMacro{test-results-3-50-model0-lc9-num-all-failrate-avg}{75.54}
\DefMacro{test-results-3-50-model0-lc9-num-all-failrate-med}{79.46}
\DefMacro{test-results-3-50-model0-lc9-num-all-failrate-std}{3.855}

@@

\DefMacro{test-results-3-50-model0-lc2-num-all-fail-avg}{251.0}
\DefMacro{test-results-3-50-model0-lc2-num-all-fail-med}{226}
\DefMacro{test-results-3-50-model0-lc2-num-all-fail-std}{80.48}
\DefMacro{test-results-3-50-model0-lc2-num-all-failrate-avg}{15.72}
\DefMacro{test-results-3-50-model0-lc2-num-all-failrate-med}{13.52}
\DefMacro{test-results-3-50-model0-lc2-num-all-failrate-std}{5.125}

@@

\DefMacro{test-results-3-50-model0-lc0-num-all-fail-avg}{219.0}
\DefMacro{test-results-3-50-model0-lc0-num-all-fail-med}{213}
\DefMacro{test-results-3-50-model0-lc0-num-all-fail-std}{7.0}
\DefMacro{test-results-3-50-model0-lc0-num-all-failrate-avg}{87.13}
\DefMacro{test-results-3-50-model0-lc0-num-all-failrate-med}{87.36}
\DefMacro{test-results-3-50-model0-lc0-num-all-failrate-std}{0.34}

@@

\DefMacro{test-results-3-50-model0-lc1-num-all-fail-avg}{6.0}
\DefMacro{test-results-3-50-model0-lc1-num-all-fail-med}{6}
\DefMacro{test-results-3-50-model0-lc1-num-all-fail-std}{0.5}
\DefMacro{test-results-3-50-model0-lc1-num-all-failrate-avg}{1.24}
\DefMacro{test-results-3-50-model0-lc1-num-all-failrate-med}{1.16}
\DefMacro{test-results-3-50-model0-lc1-num-all-failrate-std}{0.21}

@@

\DefMacro{test-results-3-50-model0-lc8-num-all-fail-avg}{79.33}
\DefMacro{test-results-3-50-model0-lc8-num-all-fail-med}{91}
\DefMacro{test-results-3-50-model0-lc8-num-all-fail-std}{15.12}
\DefMacro{test-results-3-50-model0-lc8-num-all-failrate-avg}{5.82}
\DefMacro{test-results-3-50-model0-lc8-num-all-failrate-med}{6.65}
\DefMacro{test-results-3-50-model0-lc8-num-all-failrate-std}{1.21}

@@

\DefMacro{test-results-3-50-model1-lc7-num-all-fail-avg}{297.33}
\DefMacro{test-results-3-50-model1-lc7-num-all-fail-med}{293}
\DefMacro{test-results-3-50-model1-lc7-num-all-fail-std}{13.875}
\DefMacro{test-results-3-50-model1-lc7-num-all-failrate-avg}{20.63}
\DefMacro{test-results-3-50-model1-lc7-num-all-failrate-med}{15.92}
\DefMacro{test-results-3-50-model1-lc7-num-all-failrate-std}{5.005}

@@

\DefMacro{test-results-3-50-model1-lc3-num-all-fail-avg}{1916.33}
\DefMacro{test-results-3-50-model1-lc3-num-all-fail-med}{1828}
\DefMacro{test-results-3-50-model1-lc3-num-all-fail-std}{114.34}
\DefMacro{test-results-3-50-model1-lc3-num-all-failrate-avg}{88.09}
\DefMacro{test-results-3-50-model1-lc3-num-all-failrate-med}{87.08}
\DefMacro{test-results-3-50-model1-lc3-num-all-failrate-std}{1.32}

@@

\DefMacro{test-results-3-50-model1-lc4-num-all-fail-avg}{1042.67}
\DefMacro{test-results-3-50-model1-lc4-num-all-fail-med}{1038}
\DefMacro{test-results-3-50-model1-lc4-num-all-fail-std}{7.765}
\DefMacro{test-results-3-50-model1-lc4-num-all-failrate-avg}{93.29}
\DefMacro{test-results-3-50-model1-lc4-num-all-failrate-med}{93.31}
\DefMacro{test-results-3-50-model1-lc4-num-all-failrate-std}{0.135}

@@

\DefMacro{test-results-3-50-model1-lc6-num-all-fail-avg}{839.33}
\DefMacro{test-results-3-50-model1-lc6-num-all-fail-med}{831}
\DefMacro{test-results-3-50-model1-lc6-num-all-fail-std}{23.53}
\DefMacro{test-results-3-50-model1-lc6-num-all-failrate-avg}{73.09}
\DefMacro{test-results-3-50-model1-lc6-num-all-failrate-med}{70.01}
\DefMacro{test-results-3-50-model1-lc6-num-all-failrate-std}{5.795}

@@

\DefMacro{test-results-3-50-model1-lc5-num-all-fail-avg}{1517.33}
\DefMacro{test-results-3-50-model1-lc5-num-all-fail-med}{1384}
\DefMacro{test-results-3-50-model1-lc5-num-all-fail-std}{125.56}
\DefMacro{test-results-3-50-model1-lc5-num-all-failrate-avg}{99.4}
\DefMacro{test-results-3-50-model1-lc5-num-all-failrate-med}{99.21}
\DefMacro{test-results-3-50-model1-lc5-num-all-failrate-std}{0.2}

@@

\DefMacro{test-results-3-50-model1-lc9-num-all-fail-avg}{1225.33}
\DefMacro{test-results-3-50-model1-lc9-num-all-fail-med}{1117}
\DefMacro{test-results-3-50-model1-lc9-num-all-fail-std}{166.975}
\DefMacro{test-results-3-50-model1-lc9-num-all-failrate-avg}{78.74}
\DefMacro{test-results-3-50-model1-lc9-num-all-failrate-med}{82.74}
\DefMacro{test-results-3-50-model1-lc9-num-all-failrate-std}{5.94}

@@

\DefMacro{test-results-3-50-model1-lc2-num-all-fail-avg}{744.33}
\DefMacro{test-results-3-50-model1-lc2-num-all-fail-med}{723}
\DefMacro{test-results-3-50-model1-lc2-num-all-fail-std}{71.105}
\DefMacro{test-results-3-50-model1-lc2-num-all-failrate-avg}{46.7}
\DefMacro{test-results-3-50-model1-lc2-num-all-failrate-med}{43.27}
\DefMacro{test-results-3-50-model1-lc2-num-all-failrate-std}{4.525}

@@

\DefMacro{test-results-3-50-model1-lc0-num-all-fail-avg}{200.0}
\DefMacro{test-results-3-50-model1-lc0-num-all-fail-med}{192}
\DefMacro{test-results-3-50-model1-lc0-num-all-fail-std}{7.81}
\DefMacro{test-results-3-50-model1-lc0-num-all-failrate-avg}{79.52}
\DefMacro{test-results-3-50-model1-lc0-num-all-failrate-med}{79.01}
\DefMacro{test-results-3-50-model1-lc0-num-all-failrate-std}{0.67}

@@

\DefMacro{test-results-3-50-model1-lc1-num-all-fail-avg}{14.33}
\DefMacro{test-results-3-50-model1-lc1-num-all-fail-med}{6}
\DefMacro{test-results-3-50-model1-lc1-num-all-fail-std}{7.655}
\DefMacro{test-results-3-50-model1-lc1-num-all-failrate-avg}{2.81}
\DefMacro{test-results-3-50-model1-lc1-num-all-failrate-med}{1.21}
\DefMacro{test-results-3-50-model1-lc1-num-all-failrate-std}{1.465}

@@

\DefMacro{test-results-3-50-model1-lc8-num-all-fail-avg}{81.0}
\DefMacro{test-results-3-50-model1-lc8-num-all-fail-med}{81}
\DefMacro{test-results-3-50-model1-lc8-num-all-fail-std}{14.5}
\DefMacro{test-results-3-50-model1-lc8-num-all-failrate-avg}{5.84}
\DefMacro{test-results-3-50-model1-lc8-num-all-failrate-med}{6.14}
\DefMacro{test-results-3-50-model1-lc8-num-all-failrate-std}{0.95}

@@

\DefMacro{test-results-3-50-model2-lc7-num-all-fail-avg}{490.67}
\DefMacro{test-results-3-50-model2-lc7-num-all-fail-med}{420}
\DefMacro{test-results-3-50-model2-lc7-num-all-fail-std}{98.38}
\DefMacro{test-results-3-50-model2-lc7-num-all-failrate-avg}{31.59}
\DefMacro{test-results-3-50-model2-lc7-num-all-failrate-med}{33.68}
\DefMacro{test-results-3-50-model2-lc7-num-all-failrate-std}{5.43}

@@

\DefMacro{test-results-3-50-model2-lc3-num-all-fail-avg}{1862.0}
\DefMacro{test-results-3-50-model2-lc3-num-all-fail-med}{1827}
\DefMacro{test-results-3-50-model2-lc3-num-all-fail-std}{96.94}
\DefMacro{test-results-3-50-model2-lc3-num-all-failrate-avg}{85.66}
\DefMacro{test-results-3-50-model2-lc3-num-all-failrate-med}{86.06}
\DefMacro{test-results-3-50-model2-lc3-num-all-failrate-std}{0.64}

@@

\DefMacro{test-results-3-50-model2-lc4-num-all-fail-avg}{1068.33}
\DefMacro{test-results-3-50-model2-lc4-num-all-fail-med}{1073}
\DefMacro{test-results-3-50-model2-lc4-num-all-fail-std}{8.735}
\DefMacro{test-results-3-50-model2-lc4-num-all-failrate-avg}{95.59}
\DefMacro{test-results-3-50-model2-lc4-num-all-failrate-med}{95.33}
\DefMacro{test-results-3-50-model2-lc4-num-all-failrate-std}{0.245}

@@

\DefMacro{test-results-3-50-model2-lc6-num-all-fail-avg}{1056.0}
\DefMacro{test-results-3-50-model2-lc6-num-all-fail-med}{972}
\DefMacro{test-results-3-50-model2-lc6-num-all-fail-std}{76.675}
\DefMacro{test-results-3-50-model2-lc6-num-all-failrate-avg}{90.95}
\DefMacro{test-results-3-50-model2-lc6-num-all-failrate-med}{92.95}
\DefMacro{test-results-3-50-model2-lc6-num-all-failrate-std}{4.125}

@@

\DefMacro{test-results-3-50-model2-lc5-num-all-fail-avg}{1500.0}
\DefMacro{test-results-3-50-model2-lc5-num-all-fail-med}{1382}
\DefMacro{test-results-3-50-model2-lc5-num-all-fail-std}{110.52}
\DefMacro{test-results-3-50-model2-lc5-num-all-failrate-avg}{98.45}
\DefMacro{test-results-3-50-model2-lc5-num-all-failrate-med}{99.07}
\DefMacro{test-results-3-50-model2-lc5-num-all-failrate-std}{0.97}

@@

\DefMacro{test-results-3-50-model2-lc9-num-all-fail-avg}{1235.67}
\DefMacro{test-results-3-50-model2-lc9-num-all-fail-med}{1112}
\DefMacro{test-results-3-50-model2-lc9-num-all-fail-std}{251.03}
\DefMacro{test-results-3-50-model2-lc9-num-all-failrate-avg}{78.61}
\DefMacro{test-results-3-50-model2-lc9-num-all-failrate-med}{82.37}
\DefMacro{test-results-3-50-model2-lc9-num-all-failrate-std}{10.985}

@@

\DefMacro{test-results-3-50-model2-lc2-num-all-fail-avg}{895.0}
\DefMacro{test-results-3-50-model2-lc2-num-all-fail-med}{953}
\DefMacro{test-results-3-50-model2-lc2-num-all-fail-std}{86.715}
\DefMacro{test-results-3-50-model2-lc2-num-all-failrate-avg}{55.93}
\DefMacro{test-results-3-50-model2-lc2-num-all-failrate-med}{60.58}
\DefMacro{test-results-3-50-model2-lc2-num-all-failrate-std}{4.545}

@@

\DefMacro{test-results-3-50-model2-lc0-num-all-fail-avg}{241.67}
\DefMacro{test-results-3-50-model2-lc0-num-all-fail-med}{233}
\DefMacro{test-results-3-50-model2-lc0-num-all-fail-std}{8.385}
\DefMacro{test-results-3-50-model2-lc0-num-all-failrate-avg}{96.12}
\DefMacro{test-results-3-50-model2-lc0-num-all-failrate-med}{96.28}
\DefMacro{test-results-3-50-model2-lc0-num-all-failrate-std}{0.495}

@@

\DefMacro{test-results-3-50-model2-lc1-num-all-fail-avg}{4.0}
\DefMacro{test-results-3-50-model2-lc1-num-all-fail-med}{5}
\DefMacro{test-results-3-50-model2-lc1-num-all-fail-std}{0.865}
\DefMacro{test-results-3-50-model2-lc1-num-all-failrate-avg}{0.82}
\DefMacro{test-results-3-50-model2-lc1-num-all-failrate-med}{0.86}
\DefMacro{test-results-3-50-model2-lc1-num-all-failrate-std}{0.205}

@@

\DefMacro{test-results-3-50-model2-lc8-num-all-fail-avg}{91.33}
\DefMacro{test-results-3-50-model2-lc8-num-all-fail-med}{82}
\DefMacro{test-results-3-50-model2-lc8-num-all-fail-std}{17.96}
\DefMacro{test-results-3-50-model2-lc8-num-all-failrate-avg}{6.7}
\DefMacro{test-results-3-50-model2-lc8-num-all-failrate-med}{5.99}
\DefMacro{test-results-3-50-model2-lc8-num-all-failrate-std}{1.465}
